On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-03 paper.tex
Commit before going home
We have been working on the finiteness of \delta=1, arity being at least
3.

\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 granted to S.~Z.~F. and S.~S. and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}
}
\author{
Szil\'{a}rd Zsolt Fazekas\inst{1} \and
Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
\institute{
Akita University, 
Graduate School of Engineering Science, 
1-1 Tegate Gakuen-machi, Akita, 0108502, Japan \\
%\email{szilard.fazekas@ie.akita-u.ac.jp}
\and
The University of Electro-Communications, 
Graduate School of Informatics and Engineering, 
1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
}

@@

Transcription is the first essential step of gene expression, when a DNA template sequence is copied into a complementary single stranded RNA sequence by a `copy machine' called RNA polymerase. 
The RNA strand is synthesized letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$ and folds up during a process called co-transcriptional folding.

@@

\draw[-latex] (origin) -- ++(0:3) node[below] {$\delta$}; 
\node at (1, -0.2) {1};
\node at (2, -0.2) {2};
\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
\node at (-0.2, 1) {1};
\node at (-0.2, 2) {2};
\node at (-0.2, 3) {3};
\node at (-0.2, 4) {4};

%Results
\node at (1, 4) {$O(n^2)$};
\node at (1, 3) {$O(n)$};
\node at (1, 2) {$O(n^2)$};
\node at (1, 1) {$9n$ \cite{DHOPRSST2018}};

\node at (2, 1) {$O(n^2)$};

@@

In \cite{DHOPRSST2018}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.

>>>>

\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 granted to S.~Z.~F. and S.~S. and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}
}
\titlerunning{Power of unary oritatami cotranscriptional folding}
\author{
Szil\'{a}rd Zsolt Fazekas\inst{1} \and 
Kohei Maruyama \and
Reoto Morita \and \\
Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
\institute{
Akita University, 
Graduate School of Engineering Science, 
1-1 Tegate Gakuen-machi, Akita, 0108502, Japan \\
%\email{szilard.fazekas@ie.akita-u.ac.jp}
\and
The University of Electro-Communications, 
Graduate School of Informatics and Engineering, 
1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
}

@@

Transcription is the first essential step of gene expression, in which a DNA template sequence is copied into a complementary single stranded RNA sequence by a `copy machine' called RNA polymerase. 
The RNA strand is synthesized letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$ and folds up during a process called co-transcriptional folding.

@@

\draw[-latex] (origin) -- ++(0:5) node[below] {$\delta$}; 
\node at (2, -0.2) {1};
\node at (4, -0.2) {2 and 3};
\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
\node at (-0.2, 1) {1};
\node at (-0.2, 2) {2};
\node at (-0.2, 3) {3};
\node at (-0.2, 4) {4};

%Results
\node at (2, 4) {$3n(n+1)+1$};
\node at (2, 3) {$O(n)$};
\node at (2, 2) {$O(n^2)$};
\node at (2, 1) {$10n$ \cite{DHOPRSST2018}};

\node at (4, 1) {$O(n^2)$};

@@

In \cite{DHOPRSST2018}, Demaine et al. proved that at delay 1 and arity 1, upon the seed of length $n$, a deterministic oritatami system cannot fold into any conformation strictly longer than $10n$. 
We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.
